Data Analysis Extensions

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
A few fixes to previous commit
Former-commit-id: 66a36b3bc72dbb39f4f492b15a12021995ef594e

% Code snippets
\usepackage{listings}
\def\lstsetc{\lstset{language=C,
  numbers=left,
  xleftmargin=1.8em,
  frame=L,
  framexleftmargin=0.2em,
  rulecolor=\color{rulecolor},
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  showspaces=false, 
  showstringspaces=false,
  breaklines=true,
  basicstyle=\footnotesize\ttfamily,
  stringstyle=\itshape,
  commentstyle=\itshape\bfseries,
  morekeywords={main, size_t, malloc, free,
    hsize_t, hid_t, herr_t, H5X_class_t, H5X_type_t, H5Q_combine_op_t,
    H5Q_type_t, H5Q_match_op_t,
    H5Fcreate, H5Fclose,
    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery,
    H5Qcreate, H5Qclose, H5Qcombine, H5Qget_type, H5Qget_match_op,
    H5Qget_components, H5Qget_combine_op, H5Qencode, H5Qdecode,
    H5Qapply,
    H5Screate_simple, H5Sclose, H5Sget_select_npoints,
    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count, H5Xget_size,
    H5Xget_info
    }
  }
}

>>>>

% Code snippets
\usepackage{listings}
\def\lstsetc{\lstset{language=C,
  numbers=left,
  xleftmargin=1.8em,
  frame=L,
  framexleftmargin=0.2em,
  rulecolor=\color{rulecolor},
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  showspaces=false, 
  showstringspaces=false,
  breaklines=true,
  basicstyle=\footnotesize\ttfamily,
  stringstyle=\itshape,
  commentstyle=\itshape\bfseries,
  morekeywords={main, size_t, malloc, free,
    hsize_t, hid_t, herr_t,
    H5X_class_t, H5X_type_t, H5X_info_t,
    H5Q_combine_op_t, H5Q_type_t, H5Q_match_op_t,
    H5Fcreate, H5Fclose,
    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery,
    H5Qcreate, H5Qclose, H5Qcombine, H5Qget_type, H5Qget_match_op,
    H5Qget_components, H5Qget_combine_op, H5Qencode, H5Qdecode,
    H5Qapply,
    H5Screate_simple, H5Sclose, H5Sget_select_npoints,
    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count, H5Xget_size,
    H5Xget_info
    }
  }
}
